\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-29 OaklandSubmission/eval.tex
minor

A more interesting classifier is {\em Na\"{i}ve Bayes} that predicts labels
from the set $[n]$.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
The model has two matrices: a vector $P$ of length $n$ s.t. for each
$i
\in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood
%that the output label is $i$ for $i\in[n]$.
The other matrix $T$ has size $d\times F\times n$ and for each $j\in
[d], k\in [F], i\in [n]$, the entry $T(j)(k)(i)$ is 
%\equiv\log p(x_j|\ell=i)$, i.e.,
the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
The classifier $C_{P,T}(x)$ outputs
\[
{\sf argmax}\ P+\sum_{j=0}^{d-1} T(j)(x_j)
\]
The additions in the expression above sum $n$-dimensional vectors.
The model size of this classifier is $|P|+|T|$.
This classifier requires $\Theta(ndF)$ comparisons and additions. Note here  that computing $T(j)(x_j)(i)$ requires a secret look-up in matrix  $T$  based on secret input $x_j$ resulting in $F-1$ comparisons using multiplexers (see
  Section~\ref{sec:impl}). %\nc{Made DG's comment as part of regular text - worth point out}. \cmmt{Is there a +1 etc missing or is this exact?} \nc{By our calculation in Sec 5, it seems that this should be $F/2$ multiplexers}

A {\em decision tree} of size $N$ takes as input an $x\in\R^d$, and the
model consists of a binary tree of depth $d$ with a boolean predicate
assigned to each internal node. The root note is the $0^{th}$ node and
for an internal node $j \in [N]$, the children nodes are $2j+1$ and
$2j+2$. Each internal node $j\in[N]$ at depth $i$ has a predicate
$b_{j}^i\equiv x_i\leq w_{j}$. We start evaluating the tree from the
root and if the predicate at the current node $b_j^i$ is false (resp.,
true) then $x$ is passed to the left (resp., right) child with
predicate $b_{2j+1}^{i+1}$ (resp., $b_{2j+2}^{i+1}$). This process is
repeated till we reach a leaf. The leaves of the tree are labels and
the output label is the leaf visited by this traversal.
Such a (binary) decision tree can be encoded as a polynomial (of
degree linear in depth of the tree) and then the prediction task
reduces to polynomial evaluation. E.g., a binary tree with depth one
and size $N=3$ can be encoded as the polynomial
$(1-b(x))\ell_0 + b(x)\ell_1$ where $b(x)$ is the predicate at the
root, $\ell_0$ is the label of the left leaf and $\ell_1$ is the label
of the right leaf.

@@

\subsection{State-of-the-art classifiers}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
\[
 \mathsf{argmax}\ W\matmul x+b
\]
Here, $x$ is a 784 length vector obtained from the input image,
each $W$ is a $10\times 784$ matrix, and each $b$ is a $10$ length
vector.
We implement this classifer in \tool and present the results in the
first row of Table~\ref{tab:tf}. We note that a pure boolean circuit for this simple functionality does not fit in the memory of our machines.

@@

 \caption{Bonsai benchmarks}
 \label{tab:bonsai} 
\end{table}
\setlength\tabcolsep{6pt}
\subsection{Partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines.

>>>>

A more interesting classifier is {\em Na\"{i}ve Bayes} that predicts labels
from the set $[n]$~\cite{shafindss}.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
%The model has two matrices: a vector $P$ of length $n$ s.t. for each
%$i
%\in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood
%that the output label is $i$ for $i\in[n]$.
%The other matrix $T$ has size $d\times F\times n$ and for each $j\in
%[d], k\in [F], i\in [n]$, the entry $T(j)(k)(i)$ is 
%\equiv\log p(x_j|\ell=i)$, i.e.,
%the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
%The classifier $C_{P,T}(x)$ outputs
%\[
%{\sf argmax}\ P+\sum_{j=0}^{d-1} T(j)(x_j)
%\]
%The additions in the expression above sum $n$-dimensional vectors.
%The model size of this classifier is $|P|+|T|$.
This classifier requires $\Theta(ndF)$ comparisons and additions. %Note here  that computing $T(j)(x_j)(i)$ requires a secret look-up in matrix  $T$  based on secret input $x_j$ resulting in $F-1$ comparisons using multiplexers (see
  %Section~\ref{sec:impl}). %\nc{Made DG's comment as part of regular text - worth point out}. \cmmt{Is there a +1 etc missing or is this exact?} \nc{By our calculation in Sec 5, it seems that this should be $F/2$ multiplexers}
%
A {\em decision tree} of size $N$ takes as input an $x\in\R^d$
%,
 and 
%the
%model consists of a binary tree of depth $d$ with a boolean predicate
%assigned to each internal node.
% The root note is the $0^{th}$ node and
%for an internal node $j \in [N]$, the children nodes are $2j+1$ and
%$2j+2$. Each internal node $j\in[N]$ at depth $i$ has a predicate
%$b_{j}^i\equiv x_i\leq w_{j}$. We start evaluating the tree from the
%root and if the predicate at the current node $b_j^i$ is false (resp.,
%true) then $x$ is passed to the left (resp., right) child with
%predicate $b_{2j+1}^{i+1}$ (resp., $b_{2j+2}^{i+1}$). This process is
%repeated till we reach a leaf. The leaves of the tree are labels and
%the output label is the leaf visited by this traversal.
%Such a (binary) decision tree 
%and can be encoded as a polynomial (of
%degree linear in depth of the tree) and then
 the prediction task
reduces to polynomial evaluation~\cite{shafindss}.
% E.g., a binary tree with depth one
%and size $N=3$ can be encoded as the polynomial
%$(1-b(x))\ell_0 + b(x)\ell_1$ where $b(x)$ is the predicate at the
%root, $\ell_0$ is the label of the left leaf and $\ell_1$ is the label
%of the right leaf.

@@

\subsection{State-of-the-art classifiers}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of
digits 0 to 9.
The first model that the tutorial describes is a softmax regression
that provides an accuracy of 92\%. The classifier evaluates
$ \mathsf{argmax}\ W\matmul x+b$.
Here, $x$ is a 784 length vector obtained from the input image,
each $W$ is a $10\times 784$ matrix, and each $b$ is a $10$ length
vector.
We implement this classifer in \tool and present the results in the
first row of Table~\ref{tab:tf}. We note that a pure boolean circuit for this simple functionality does not fit in the memory of our machines.

@@

 \caption{Bonsai benchmarks}
 \label{tab:bonsai} 
\end{table}
\setlength\tabcolsep{6pt}
\subsection{Partitioning}
\label{sec:pipeeval}
We evaluate partitioning next.
\subsubsection*{CIFAR-10}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines.
